What if you drop that? Modeling children's curiosity about physical interactions

### 2020-01-15 paper/paper.Rmd
some figures

---
#title: "Modeling children's intrinsically-motivated curiosity about object interactions"
title: "What if you drop that? Modeling children's curiosity about physical interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

```{r, load-data}
raw = read.csv2("../analysis/human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T)
hum = subset(raw, Exclude!="Y") # 577 trials

@@

### Participants
Participants were `r length(unique(raw$SID))` children recruited from the Children's Discovery Museum of San Jose and Bing Nursery School.
Exclusions were made based on...
After exclusions, results from `r length(hum$SID)` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.

@@

@@

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

@@

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                       caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

>>>>

---
#title: "Modeling children's intrinsically-motivated curiosity about object interactions"
#title: "Drop it like it's hot: Modeling children's curiosity about physical interactions"
#title: "A drop in the bucket: Modeling children's curiosity about physical interactions"
title: "What if you drop that? Modeling children's curiosity about physical interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

```{r, load-data}
raw = read.csv2("../analysis/human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T, stringsAsFactors=F)
hum = subset(raw, Exclude!="Y")

hum = hum[-which(hum$StimSet=="bc" & hum$DropChoice=="bowl and dumbbell"),] # chose two - exclude

@@

### Participants
Participants were `r length(unique(raw$SID))` children recruited from the Children's Discovery Museum of San Jose and Bing Nursery School.
Exclusions were made based on...
After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.

@@

```{r object-sets}
shapes = c("bowl","cone","dumbbell","octahedron","pentagon","pipe","pyramid","torus","trig prism")

a = c("pyramid", "torus", "trig prism")
b = c("cone", "octahedron", "pipe")
c = c("bowl", "dumbbell", "pentagon")
```

@@

We first examine children's choice of drop objects and target objects to see if children had any preference for particular objects.

```{r drop-choice, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
ch_cond <- hum %>% 
  group_by(StimSet, DropChoice) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
  geom_point(alpha=.8) +
  scale_shape_manual(values=10:19) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,.66) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  geom_hline(yintercept=.33, lty='dashed')
```

```{r target-hit, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
hum$Target = hum$DropLocation
ch_cond <- hum %>% 
  filter(Target!="outside") %>%
  group_by(StimSet, Target) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes, "space"))
ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
  geom_point(alpha=.8) +
  scale_shape_manual(values=10:20) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Stimulus Set") + ylab("Rate of Target Object Choice") + ylim(0,.66) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  geom_hline(yintercept=.33, lty='dashed')
```

```{r target-space, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}

hum$TargetSpace = ifelse(hum$DropLocation=="space", hum$WhichSpace, hum$DropLocation)

ch_cond <- hum %>% 
  filter(is.element(TargetSpace, shapes)) %>%
  group_by(StimSet, TargetSpace) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

ch_cond$TargetSpace <- factor(ch_cond$TargetSpace, levels = shapes)
ggplot(ch_cond, aes(x=StimSet, y=freq, shape=TargetSpace, color=TargetSpace)) + # , size=n
  geom_point(alpha=.8) +
  scale_shape_manual(values=10:19) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Stimulus Set") + ylab("Rate of Target Location Choice") + ylim(0,.66) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  geom_hline(yintercept=.33, lty='dashed')
```

@@
